Computing properties of independent sets by generic programming tensor networks \thanks{\funding{...}}

### 2022-01-22 paper/paper.tex
grammar fixes for appendix A

\section{Technical guide}\label{sec:technical}
This project depends on multiple open source packages in Julia ecosystem.
We list the Julia packages playing important roles in our code base as follows.

\begin{description}
	\item[\href{https://github.com/under-Peter/OMEinsum.jl}{OMEinsum} and \href{https://github.com/Happy-Diode/OMEinsumContractionOrders.jl}{OMEinsumContractionOrders}] are packages providing the support for Einstein's (or tensor network) notation and contraction order optimizations.
    \texttt{OMEinsumContractionOrders} implements state of art algorithms for finding the optimal contraction order for the an tensor network, including the KaHypar+Greedy~\cite{Gray2021, Pan2021} and local transformation based approaches~\cite{Kalachev2021},
	\item[\href{https://github.com/TensorBFS/TropicalNumbers.jl}{TropicalNumbers} and \href{https://github.com/TensorBFS/TropicalGEMM.jl}{TropicalGEMM}] are packages providing tropical number and efficient tropical matrix multiplication,
	\item[\href{https://github.com/JuliaGraphs/Graphs.jl}{Graphs}] is a package providing graph utilities, like random regular graph generator,
	\item[\href{https://github.com/JuliaMath/Polynomials.jl}{Polynomials}] is a package providing polynomial algebra and polynomial fitting,
	\item[\href{https://github.com/scheinerman/Mods.jl}{Mods} and \href{https://github.com/JuliaMath/Primes.jl}{Primes}] are packages providing finite field algebra and prime number generations.
\end{description}

@@

It may surprise you that the Julia implementation of algorithms introduced in the paper is so short that except the bounding algorithm,
all are contained in this appendix. After installing required packages, one can open a Julia REPL and copy the following code into it.

@@

For performance reason, we still recommend checking our GitHub repository for the full featured version:
\href{https://github.com/Happy-Diode/GraphTensorNetworks.jl}{https://github.com/Happy-Diode/GraphTensorNetworks.jl}.
It can be installed in a similar style to other packages. Here is a short introduction to the functionalities in this package.

>>>>

\section{Technical guide}\label{sec:technical}
This project depends on multiple open source packages in the Julia ecosystem.
We list the Julia packages that play important roles in our code base as follows:

\begin{description}
	\item[\href{https://github.com/under-Peter/OMEinsum.jl}{OMEinsum} and \href{https://github.com/Happy-Diode/OMEinsumContractionOrders.jl}{OMEinsumContractionOrders}] are packages providing the support for Einstein's (or tensor network) notation and contraction order optimizations.
    \texttt{OMEinsumContractionOrders} implements state-of-the-art algorithms for finding the optimal contraction order for a tensor network, including the KaHypar+Greedy~\cite{Gray2021, Pan2021} and local transformation based approaches~\cite{Kalachev2021},
	\item[\href{https://github.com/TensorBFS/TropicalNumbers.jl}{TropicalNumbers} and \href{https://github.com/TensorBFS/TropicalGEMM.jl}{TropicalGEMM}] are packages providing tropical number and efficient tropical matrix multiplication,
	\item[\href{https://github.com/JuliaGraphs/Graphs.jl}{Graphs}] is a package providing graph utilities, like random regular graph generator,
	\item[\href{https://github.com/JuliaMath/Polynomials.jl}{Polynomials}] is a package providing polynomial algebra and polynomial fitting,
	\item[\href{https://github.com/scheinerman/Mods.jl}{Mods} and \href{https://github.com/JuliaMath/Primes.jl}{Primes}] are packages providing finite field algebra and prime number generations.
\end{description}

@@

The reader may find it surprising that the Julia implementation of the algorithms introduced in this work is so short that except the bounding algorithm,
all are contained in this appendix. This is due to the power of generic programming. After installing the required packages, one can open a Julia REPL and copy the following codes into it.

@@

For better performance, we recommend checking our GitHub repository for the full featured version:
\href{https://github.com/Happy-Diode/GraphTensorNetworks.jl}{https://github.com/Happy-Diode/GraphTensorNetworks.jl}.
It can be installed in a similar style to other packages. Here is a short introduction to the functionalities in this package.
